
\section*{Acknowledgment}


Work was in part funded by the NSF CyberTraining: CIC: CyberTraining for Students and Technologies from Generation Z with the award numbers 1829704 and 2200409 and NIST 60NANB21D151T.  The work was also funded by the Department of Energy under the grant Award No. DE-SC0023452. The work was conducted at the Biocomplexity Institute and Initiative at the University of Virginia.

This research was sponsored in part by and used resources of the Oak Ridge Leadership Computing Facility (OLCF), which is a DOE Office of Science User Facility at the Oak Ridge National Laboratory (ORNL) supported by the U.S. Department of Energy under Contract No. DE-AC05-00OR22725. Kirkpatrick's work was made possible through the National Science Foundation award \#2226453. Shao was supported by internal funding from Hewlett Packard Enterprise. He additionally gratefully acknowledges the contributions of SmartSim developers, specifically Alyssa Cote for providing a figure used in this paper.


\cite{las-2023-mlcommons-edu-eq}

Research was sponsored by the Department of the Air Force Artificial
Intelligence Accelerator and was accomplished under Cooperative
Agreement Number FA8750-19-2-1000. The views and conclusions contained
in this document are those of the authors and should not be interpreted
as representing the official policies, either expressed or implied, of
the Department of the Air Force or the U.S.\ Government. The U.S.\
Government is authorized to reproduce and distribute reprints for
Government purposes notwithstanding any copyright notation herein.
%\input{energy}

We have used ``ChatGPT'' to improve upon the grammar of selected section with the question: ``Improve the grammar of ...''