
\section*{Acknowledgment}

\TODO{we need to update the acknowledgment section. IN order to avoid confusion we will write a complete new one and you are supposed to add test to the new acknowledgment while removing the once no longer used form the old so we no longer need to worry about it.}


New Acknowledgement:

PUT YOUR TEXT HERE AND DO NOT FORGET TO REMOVE IT FROM THE OLD.


We have used ``ChatGPT'' to improve upon the grammar of selected section with the question: ``Improve the grammar of ...''

% Wisconsin ACKs
The portion of this work done at UW-Madison is supported in part by NSF grant CNS-2312688 and by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research, under Award Number DE-SC-0026036.

% Fermi (Ben & Nhan) Acks
This manuscript has been in part authored by FermiForward Discovery Group, LLC under Contract No. 89243024CSC000002 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
Fermilab Report Number FERMILAB-PUB-25-0835-CSAID. 

This work was supported by DOE ASCR Microelectronics Science Research Center Projects, BIA.  This material is based upon work supported by the U.S. Department of Energy, Office of Science, under contract number DE-AC02-06CH11357.

% Marco Acks
This work was partially supported by the NSF POSE Phase II Award 2303700.


\TODO{remove yours once you have added yours to the New Acknowledgement section: Old Acknowledgement:
Work was in part funded by the NSF CyberTraining: CIC: CyberTraining for Students and Technologies from Generation Z with the award numbers 1829704 and 2200409 and NIST 60NANB21D151T.  The work was also funded by the Department of Energy under the grant Award No. DE-SC0023452. The work was conducted at the Biocomplexity Institute and Initiative at the University of Virginia.

This research was sponsored in part by and used resources of the Oak Ridge Leadership Computing Facility (OLCF), which is a DOE Office of Science User Facility at the Oak Ridge National Laboratory (ORNL) supported by the U.S. Department of Energy under Contract No. DE-AC05-00OR22725. Kirkpatrick's work was made possible through the National Science Foundation award \#2226453. Shao was supported by internal funding from Hewlett Packard Enterprise. He additionally gratefully acknowledges the contributions of SmartSim developers, specifically Alyssa Cote for providing a figure used in this paper.


\cite{las-2023-mlcommons-edu-eq}

Research was sponsored by the Department of the Air Force Artificial
Intelligence Accelerator and was accomplished under Cooperative
Agreement Number FA8750-19-2-1000. The views and conclusions contained
in this document are those of the authors and should not be interpreted
as representing the official policies, either expressed or implied, of
the Department of the Air Force or the U.S.\ Government. The U.S.\
Government is authorized to reproduce and distribute reprints for
Government purposes notwithstanding any copyright notation herein.
%\input{energy}
}