\section{Contributions}
\label{sec:contrib}

\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}

\newcommand{\AUTHOR}[2]{%
    \item \textbf{%
        \ifthenelse{\equal{#2}{notified}}%
            {\textcolor{darkgreen}{ \checkmark #1}}%
            {\textcolor{red}{x #1}}%
    }%
}

\TODO{please improve and correct. I am sure you have done more that we forgot, but please make sure to keep it short.}
\bigskip

Authors with \verb|{TODO}| behind their names have send a mail to 

\bigskip

\begin{verbatim}
Subject: CARPENTRY PAPER AUTHOR PERMISSION

Gregor:


- [x] I have participated in the paper writing
- [x] I want to be an author on the paper

My contributions are as follows:
- [x] I participated in the discussions in 
      the working group
- [ ] I have .... (put your contribution here

The text I like to see in the paper for 
my contributions is:

- [x] ...
    
\end{verbatim}

Instructions: Add an x to all that apply and remove the 
once that do not apply. It is your responsibility to complete this. If it is not completed, I need to remove you from the author list. This is mandated by the publisher and even arXiv.
Send the form to \href{mailto:laszewski@gmail.com}{laszewski@gmail.com} %\mailto{laszewski@gmail.com}

\bigskip

\begin{itemize}
    
\AUTHOR{Gregor von Laszewski}{notified} is the lead author of the paper. He identified first that efforts in benchmark carpentry and democratization are needed. He has lead the organization of this paper in the MLCommons Science Working Group. He also created the initial version of \cite{www-las-mlcommons-benchmark-coolection} which is related and relevant to this effort.

\AUTHOR{Piotr Luszczek}{notified} has contributed to integration of many
decades of experiences from designing, implementing, running, and
collecting results from HPC benchmarks.

\AUTHOR{Wesley Brewer}{TODO} has contributed to the simulation section.

\AUTHOR{Jeyan Thiyagalingam}{TODO} has contributed to an early version of the paper and improvements.

\AUTHOR{Juri Papay}{TODO} has contributed to an early version of the paper and improvements. The experiences and discussions with Gregor von Laszewski around the cloudmask benchmark have significantly contributed to this effort.

\AUTHOR{Geoffrey C. Fox}{notified} is leading the MLCommons Scince Working group and has contributed to many of the ideas. The experiences and discussions with Gregor von Laszewski around improvements to the earthquake benchmark have significantly contributed to this effort. The educational effort of using the earthquake benchmark with a number of students motivated this effort.

\AUTHOR{Armstrong Foundjem}{notified} has provided an early version and led the Energy section, and has contributed to the paper writing and overall improvement.

\AUTHOR{Gregg Barrett}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Murali Emani}{notified} has participated in discussions as part of the working group meetings and improved the paper.

\AUTHOR{Shirley Moore}{TODO} has worked on the performance tuning and monitoring section.

\AUTHOR{Vijay Janapa Reddi}{TODO} has participated in discussions as part of the working group meetings and improved the paper.

\AUTHOR{Gavin Farrell}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Matthew D. Sinclair}{notified} has worked on the contents dealing with variability and simulation.

\AUTHOR{Christine Kirkpatrick}{TODO} has worked on FAIR related aspects.

\AUTHOR{Shivaram Venkataraman}{notified} has worked on the contents dealing with variability.

\AUTHOR{Rutwik Jain}{notified} has worked on the contents dealing with variability.

\AUTHOR{Kartik Mathur}{notified} Has worked on improving an early version of the Energy section.

\AUTHOR{Victor Lu}{TODO} Has participated in discussions of database integration into AI benchmarks.

\AUTHOR{Tianhao Li}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Sebastian Lobentanzer}{TODO} Has worked on improving the abstract.

\AUTHOR{Sujata Goswami}{TODO} has worked on the MLCommons benchmark details in Table I.

\AUTHOR{Khojasteh Z. Mirza}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Abdulkareem Alsudais}{notified} has reviewed the motivation to AI Benchmark Carpentry and contributed to the writing of this paper.

\AUTHOR{Kongtao Chen}{TODO} has worked on the monitoring sections, related benchmarks, and participated in discussions as part of the working group meetings.

\AUTHOR{Sasidhar Kunapuli}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Tejinder Singh}{notified} has edited and improved AI hardware benchmarking and infrastructure sections and provided new KPIs for AI hardware benchmarking.

\AUTHOR{Kirsten Morehouse}{TODO} has participated in discussions as part of the working group meetings.

\AUTHOR{Sasidhar Kunapuli}{TODO} has participated in discussions as part of the working group meetings.

\end{itemize}
